### 2016-07-29 Theorem1_FP.tex
Theorem 2 proof in old syntax

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$\calS \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr \Func(\univ,[m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

>>>>

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$\calS \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr Func(\univ, [m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

### 2016-07-29 Theorem2_FP.tex
Theorem 2 proof in old syntax

\newcommand{\FK}{F_K(\langle j,x \rangle)}
\newcommand{\rhoK}{\rho(\langle j,x \rangle)}
\fixme{Clean up to match style, language and typesetting (macros,
  especially) of previous theorem.}\acnote{Modified.}

Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the private hash functions of the $\HashOracle'$s algorithm are $h_j(x) = \FK, \, j \in [1,k]$. Informally, if F is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{lin}}$ is secure against adaptive FP-finding adversaries.
\begin{theorem}\label{thm2}
Fix $k,m,n >0$. Let $B_{\mathrm{lin}}$ be the hash based filter just described. If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{lin},t}}{\cdot}$, then there exists an adversary $B$ attacking the PRF game such that
\begin{equation}
\AdvFPSecHash{B_\mathrm{lin},t}{A}\leq  \AdvPRF{F}{B}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
\end{equation}
Before giving the proof, it should be noted that $\FK$ provides domain separation and hence mutual independence, unlike hash functions in \Cref{thm1}
\end{theorem}

\begin{proof}[\Cref{thm2}]
We use a game playing argument similar to \Cref{thm1} to prove this theorem. In \game{0}(A), adversary attacks the FP game with private hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$.
\begin{equation}
\AdvFPSecHash{B_\mathrm{lin},t}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
\end{equation}
\noindent
\game{1}(A) simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$ with a random function $\rho \getsr Func(\univ,[m])$ used to generate uniformly random  hash-indices with domain separation, of elements $x \in \univ$. In $\game{2}(A)$, $t$ elements are sampled from the set of queries and tested for false positives.  The three games are shown in \Cref{fig:GameT2}.

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.99}{
\hpagesssl{.34}{.34}{.31}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \FK$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \rhoK $\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{2}(A)}\\
$\calY \gets \emptyset $\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
$z_1,\cdots, z_t \getsr \calY $\\
if $\exists i\in[1,t] \, \mbox{s.t.} \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$\calY \gets \calY \cup x$\\
Ret $\Qry^{\HashOracle}(M,x)$\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \rhoK$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{\Cref{thm2}:Game playing argument}\label{fig:GameT2}
\end{figure}

\noindent
In \Cref{fig:BGame1T2}, adversary $B$ simulates $\game{0}(A)$ and $\game{1}(A)$ for $b=1$ and $b=0$ respectively .

%\caption{Adversary $B$ and $A'$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B^{\calO}}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge \calO(\langle j,x \rangle)$, for $j\in[1,k]$\\
}
{
$\adversaryv{A'^{\HashOracle}}$\\
$\calY \gets \emptyset $ \\
$\ell \getsr [q]$\\
$c = 0$\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge c = c + 1$\\
\nudge if $c == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
$\nudge$ $\nudge \calY \gets \calY \cup x$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calZ'$\\
\nudge $z \gets \calY$\\
\nudge if $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
%
\oracle{$\HashOracle(x)$}\\
$\mathrm{Ret} \nudge \rhoK$
}
}
\caption{\Cref{thm2}:Adversary $B$ and $A'$ simulating $\game{0}(A)$, $\game{1}(A)$ and $\game{2}(A)$ respectively }\label{fig:BGame1T2}
\end{figure}

\begin{align}
\Prob{\ExpPRF{F}{B} = 1|b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1T2}\\
\Prob{\ExpPRF{F}{B} = 1|b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m2T2}
\end{align}

\noindent
From \Cref{eq:m1T2,eq:m2T2},
\begin{align}
\nonumber \Prob{\ExpPRF{F}{B} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
 \AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1T2}
\end{align}

\noindent
Following a similar argument from \Cref{thm1}\fixme{For $t>1$, proof fails for $t>1$}\acnote{Modified.}
\begin{equation}
\Prob{\game{1}(A)=1} = \frac{1}{\dbinom{q}{t}}\times\Prob{\game{2}(A)=1}\label{eq:3T2}
\end{equation}

\begin{align}
\nonumber \Prob{\game{2}(A)=1} &= q\Prob{A' \mbox{outputs FP}}\\
& \leq q \times (1-e^{-kn/m})^k \label{eq:4T2}
\end{align}

\noindent
From \Cref{eq:0T2,eq:1T2,eq:3T2,eq:4T2}: \\
\begin{align}
\nonumber \AdvFPSecHash{B_\mathrm{lin},t}{A} &- \Prob{\game{1}(A)=1} =  \AdvPRF{F}{B}   \\
\nonumber \AdvFPSecHash{B_\mathrm{lin},t}{A}  &=  \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}  \\
\AdvFPSecHash{B_\mathrm{lin},t}{A} &\leq  \AdvPRF{F}{B}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
\end{align}

>>>>

\newcommand{\FK}{F_K(\langle j,x \rangle)}
\newcommand{\rhoK}{\rho(\langle j,x \rangle)}

\fixme{Clean up to match style, language and typesetting (macros,
  especially) of previous theorem.}

Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the hash functions are defined as $h_j(x) = \FK, \, j \in [1,k]$. Informally, the following result shows, if F is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.

\begin{theorem}\label{thm2}
Fix $k,m,n >0$. Let $B_{\mathrm{ds}}$ be the hash based filter described earlier. If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{ds},t}}{\cdot}$ asking $q \times r$ queries in $t$ time, then there exists an adversary $B$ attacking the PRF game in time $O(t)$ and asking same number of queries as $A$ such that 
\begin{equation}
\AdvFPSecHash{B_\mathrm{ds},t}{A}\leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\end{equation}
\end{theorem}

\acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $. This bound which we picked from KM's theorem 6.2, is a particular case (double hashing scheme).  Theorem 6.1, on the other hand holds good for any hashing scheme that satisfies Lemma 4.1. \\
 I tried to give the FP-bound as a Lemma. 
\begin{lemma}\label{lemma1}
Fix $k,m,n >0$. The FP-error of hash-based filter $B_{\mathrm{ds}}$ with hash functions $h_j(x) = \FK, \, j \in [k]$ is upperbounded by $(1-e^{-kn/m})^k + O(1/n)$.
\end{lemma}
}
\acnote{As I had told you earlier, I was not able to understand the proofs of KM paper and now I am stuck in this proof. 
\begin{proof}($Lemma$ \ref{lemma1})
In \ref{KM}, $Theorem \,6.1$ gives the upperbound of FP error of any hashing scheme satisfying the 5 conditions enlisted in Lemma 4.1, and all these conditions are satisfied by $B_{\mathrm{ds}}$ as shown below.\\
Since the hash functions of $B_{\mathrm{ds}}$ provide randomness with domain separation and the number of hash functions are controlled by parameter $j$, condition 1 and 2 are trivially satisfied. The last condition is also trivial, since size of $B_{\mathrm{ds}}$ will be some constant multiple of size of $S$, as in the classical bloom filter.\\
The satisfiability of remaining 2 conditions is non-trivial ...
\end{proof}}
%
\begin{proof}[\Cref{thm2}]
We use a game playing argument similar to \Cref{thm1} to prove this theorem. In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{ds},r}{A}$.
\begin{equation}
\AdvFPSecHash{B_\mathrm{ds},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
\end{equation}
\noindent
\game{1}(A), \game{2}(A), and \game{3}(A) are same as in the previous theorem, except the hash-functions are distinct random functions. The non-adaptive counterparts of $B_\mathrm{ds}$ as well as the prf adversary are  identical to those of $B_\mathrm{lin}$. As shown in \game{1}(A) and \game{2}(A), the $\HashOracle$ oracle returns distinct random values in these simulations. $B$, on the other hand uses its oracle to generate random values (for $b=0$) in the following way, $h_j(x) = \calO(\langle j,x \rangle)$.

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \FK$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \rhoK $\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{{$\game{2}(A)$},\fbox{$\game{3}(A)$}}\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\bad \gets \false$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then Ret 0\\
if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
\nudge if $\bad=\true$ then \fbox{Ret 0}\\
\nudge Ret 1\\
Ret 0\\\\
%
\oracle{$\QryOracle(x)$}\\
%$\calY \gets \calY \cup \{x\}$\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,x)$\\
if $c \in \mathcal{I}$ and $v\neq 1$ then\\
\nudge $\bad \gets \true$ \\
%\nudge \fbox{Ret 1} \\
if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
\nudge $\bad \gets \true$\\
%\nudge \fbox{Ret 0}\\
Ret~$v$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to~$k$\\
\nudge $v_i  \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
\underline{$\game{4}(A)$}\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\calY \gets \emptyset$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
\nudge Ret 0\\
if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
\nudge Ret 1\\
Ret 0\\\\
%
\oracle{$\QryOracle(x)$}\\
$c \gets c+1$\\
if $c \in \mathcal{I}$ then\\
\nudge $\calY \gets \calY \cup {x}$\\
\nudge Ret 1\\
else\\
\nudge Ret 0 \\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to~$k$\\
\nudge $v_i  \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm2}: Game playing argument}\label{fig:GameT2}
\end{figure}
\noindent
Using analysis of previous theorem and \Cref{lemma1}\acnote{change if lemma1 not required}, we have
\begin{align}\label{eq:1T2}
\AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \\
\Prob{\game{1}(A)=1} &= \Prob{\game{2}(A)=1}\\
\Prob{\game{3}(A)=1} &= \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
\Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1}\\
\Prob{\game{4}(A)=1} & \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r
\end{align}

\noindent
From \Cref{eq:0T2,eq:1T2}
\begin{align}
\nonumber \AdvPRF{F}{B} &= \AdvFPSecHash{B_\mathrm{ds},r}{A} - \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
\nonumber \AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} + \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
\nonumber \AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} +  \dbinom{q}{r}\Prob{\game{4}(A)=1}\\
\AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} +  \dbinom{q}{r}\Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r
\end{align}
